Theory of surface second-harmonic generation for semiconductors including effects of nonlocal operators

### 2014-11-20 paper-v-0.tex
no errors any more! ready for last format

\title{Theory of surface second-harmonic generation for semiconductors
including effects of nonlocal operators}
\author{Sean M. Anderson}
\affiliation{Centro de Investigaciones en Optica, Le\'on, Guanajuato, M\'exico}
\author{Nicolas Tancogne-Dejean}
\affiliation{Laboratoire des Solides Irradi\'es, \'Ecole 
  Polytechnique, CNRS, CEA/DSM, 91128 Palaiseau, France}
\affiliation{European Theoretical Spectroscopy Facility (ETSF), Palaiseau, France}
\author{Bernardo S. Mendoza}\email{bms@cio.mx}
\affiliation{Centro de Investigaciones en Optica, Le\'on, Guanajuato, M\'exico}
\author{Val\'erie V\'eniard}
\affiliation{Laboratoire des Solides Irradi\'es, \'Ecole 
  Polytechnique, CNRS, CEA/DSM, 91128 Palaiseau, France}
 \affiliation{European Theoretical Spectroscopy Facility (ETSF), Palaiseau, France}

@@

We take Eq.~\eqref{vnl} into Eq.~\eqref{vcali}
and use
$\sum_{\mathbf{G}} | \mathbf{k}+\mathbf{G}\rangle \langle\mathbf{k}+\mathbf{G} | =1$, 
with
$\langle\mathbf{r}|\mathbf{k}+\mathbf{G}=(1/\sqrt{\Omega})
\mathrm{exp}(i(\mathbf{k}+\mathbf{G})\cdot\mathbf{r})$
to obtain,
\begin{align}\label{vnl.5}
\boldsymbol{\mathcal{\cal V}}^{\mathrm{nl}}_{nm}(\mathbf{k})&=\frac{1}{2}
\sum_{\mathbf{G}}
\Big(
\langle n\mathbf{k} | {\mathbf{\cal C}}(z) 
| \mathbf{k}+\mathbf{G}\rangle\langle\mathbf{k}+\mathbf{G} |
\mathbf{v}^\mathrm{nl} | m\mathbf{k}\rangle
+
\langle n\mathbf{k} |
\mathbf{v}^\mathrm{nl}  
| \mathbf{k}+\mathbf{G}\rangle\langle\mathbf{k}+\mathbf{G} |
{\mathbf{\cal C}}(z) | m\mathbf{k}\rangle
\Big)
\nonumber\\
&=\frac{1}{2 \hbar}
\sum_{\mathbf{G}}
\left(
{\mathbf{\cal F}}^{\ell*}_{n\mathbf{k}}(\mathbf{G}) 
H_{m\mathbf{k}}(\mathbf{G}) 
+
H^*_{n\mathbf{k}}(\mathbf{G}) 
{\mathbf{\cal F}}_{m\mathbf{k}}(\mathbf{G}) 
\right) 
,
\end{align}  
where 
we have defined  
\begin{align}\label{vnl.10}
{\mathbf{\cal F}}_{n\mathbf{k}}(\mathbf{G}) 
=
\sum_{\mathbf{G}'} 
A_{n\mathbf{k}}(\mathbf{G}') 
\delta_{\mathbf{G}_\parallel \mathbf{G}'_\parallel}f(G'_\perp-G_\perp) 
,
\end{align} 
\begin{align}\label{vnl.11}
H_{n\mathbf{k}}(\mathbf{G})&=
\sum_{\mathbf{G}'} 
A_{n\mathbf{k}}(\mathbf{G}') 
(\nabla_{\mathbf{K}}+\nabla_{\mathbf{K}'})  
V^\mathrm{nl}(\mathbf{K},\mathbf{K}')
,
\end{align}
and $\mathbf{K}=\mathbf{k}+\mathbf{G}$, $\mathbf{K}'=\mathbf{k}+\mathbf{G}'$.
For fully  separable pseudopotentials in the   
Kleinman-Bylander (KB) form,\cite{mottaCMS10,kleinmanPRL82,adolphPRB96}  
the  
matrix elements 
 $\langle\mathbf{K} |
V^\mathrm{nl}  
| \mathbf{K}'\rangle
=V^\mathrm{nl}(\mathbf{K},\mathbf{K}')  
$ 
and their $\mathbf{K}$ and $\mathbf{K}'$ gradient 
can be readily calculated.\cite{mottaCMS10,adolphPRB96,gordienkoRPJ04,fuchsCPC99} 
We have 
implemented 
the calculation of $\boldsymbol{\mathcal{\cal V}}^{\mathrm{nl}}_{nm}(\mathbf{k})$ with the help of 
the DP${\texttrademark}$~code.\cite{francesco}
We obtain $\mathbf{v}^{\mathrm{nl}}_{nm}(\mathbf{k})$ from the previous three 
expressions by taking ${\mathbf{\cal C}}(z)=1$, which implies 
that $f(G_\perp)=\delta_{G_\perp 0}$, 
and 
${\mathbf{\cal F}}_{n\mathbf{k}}(\mathbf{G}) \to F_{n\mathbf{k}}(\mathbf{G})=A_{n\mathbf{k}}(\mathbf{G})$.

>>>>

\title{Theory of surface second-harmonic generation for 
       semiconductors including effects of nonlocal operators}

\author{Sean M. Anderson}
    \affiliation{Centro de Investigaciones en Optica, 
                Le\'on, Guanajuato, M\'exico}
\author{Nicolas Tancogne-Dejean}
    \affiliation{Laboratoire des Solides Irradi\'es, \'Ecole Polytechnique, 
                CNRS, CEA/DSM, 91128 Palaiseau, France}
    \affiliation{European Theoretical Spectroscopy Facility (ETSF), 
                Palaiseau, France}
\author{Bernardo S. Mendoza}\email{bms@cio.mx}
    \affiliation{Centro de Investigaciones en Optica, 
                Le\'on, Guanajuato, M\'exico}
\author{Val\'erie V\'eniard}
    \affiliation{Laboratoire des Solides Irradi\'es, \'Ecole Polytechnique, 
                CNRS, CEA/DSM, 91128 Palaiseau, France}
    \affiliation{European Theoretical Spectroscopy Facility (ETSF), 
                Palaiseau, France}

@@

We take Eq.~\eqref{vnl} into Eq.~\eqref{vcali}
and use
$\sum_{\mathbf{G}} | \mathbf{k}+\mathbf{G}\rangle \langle\mathbf{k}+\mathbf{G} | =1$, 
with
$\langle\mathbf{r}|\mathbf{k}+\mathbf{G}=(1/\sqrt{\Omega})
\mathrm{exp}(i(\mathbf{k}+\mathbf{G})\cdot\mathbf{r})$
to obtain,
\begin{align}\label{vnl.5}
\boldsymbol{\mathcal{\cal V}}^{\mathrm{nl}}_{nm}(\mathbf{k})&=\frac{1}{2}
\sum_{\mathbf{G}}
\Big(
\langle n\mathbf{k} | {\mathbf{\cal C}}(z) 
| \mathbf{k}+\mathbf{G}\rangle\langle\mathbf{k}+\mathbf{G} |
\mathbf{v}^\mathrm{nl} | m\mathbf{k}\rangle
+
\langle n\mathbf{k} |
\mathbf{v}^\mathrm{nl}  
| \mathbf{k}+\mathbf{G}\rangle\langle\mathbf{k}+\mathbf{G} |
{\mathbf{\cal C}}(z) | m\mathbf{k}\rangle
\Big)
\nonumber\\
&=\frac{1}{2 \hbar}
\sum_{\mathbf{G}}
\left(
{\mathbf{\cal F}}^{\ell*}_{n\mathbf{k}}(\mathbf{G}) 
H_{m\mathbf{k}}(\mathbf{G}) 
+
H^*_{n\mathbf{k}}(\mathbf{G}) 
{\mathbf{\cal F}}_{m\mathbf{k}}(\mathbf{G}) 
\right) 
,
\end{align}  
where 
we have defined  
\begin{align}\label{vnl.10}
{\mathbf{\cal F}}_{n\mathbf{k}}(\mathbf{G}) 
=
\sum_{\mathbf{G}'} 
A_{n\mathbf{k}}(\mathbf{G}') 
\delta_{\mathbf{G}_\parallel \mathbf{G}'_\parallel}f(G'_\perp-G_\perp) 
,
\end{align} 
\begin{align}\label{vnl.11}
H_{n\mathbf{k}}(\mathbf{G})&=
\sum_{\mathbf{G}'} 
A_{n\mathbf{k}}(\mathbf{G}') 
(\nabla_{\mathbf{K}}+\nabla_{\mathbf{K}'})  
V^\mathrm{nl}(\mathbf{K},\mathbf{K}')
,
\end{align}
and $\mathbf{K}=\mathbf{k}+\mathbf{G}$, $\mathbf{K}'=\mathbf{k}+\mathbf{G}'$.
For fully  separable pseudopotentials in the   
Kleinman-Bylander (KB) form,\cite{mottaCMS10,kleinmanPRL82,adolphPRB96}  
the  
matrix elements 
 $\langle\mathbf{K} |
V^\mathrm{nl}  
| \mathbf{K}'\rangle
=V^\mathrm{nl}(\mathbf{K},\mathbf{K}')  
$ 
and their $\mathbf{K}$ and $\mathbf{K}'$ gradient 
can be readily calculated.\cite{mottaCMS10,adolphPRB96,gordienkoRPJ04,fuchsCPC99} 
We have 
implemented 
the calculation of $\boldsymbol{\mathcal{\cal V}}^{\mathrm{nl}}_{nm}(\mathbf{k})$ with the help of 
the DP\texttrademark~code.\cite{francesco}
We obtain $\mathbf{v}^{\mathrm{nl}}_{nm}(\mathbf{k})$ from the previous three 
expressions by taking ${\mathbf{\cal C}}(z)=1$, which implies 
that $f(G_\perp)=\delta_{G_\perp 0}$, 
and 
${\mathbf{\cal F}}_{n\mathbf{k}}(\mathbf{G}) \to F_{n\mathbf{k}}(\mathbf{G})=A_{n\mathbf{k}}(\mathbf{G})$.
